%==========================================================
% Shivam Gupta — Resume tailored for Stackmentalist
% Role: Python Full Stack Developer (Internship/PPO, 2027 batch, Pune)
% ATS-safe: single column, standard sections, selectable text.
% Single page. Compiles on Overleaf with pdfLaTeX/XeLaTeX. No images.
%==========================================================
\documentclass[a4paper,10pt]{article}

\usepackage[top=1cm,bottom=1cm,left=1.4cm,right=1.4cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}

\definecolor{accent}{HTML}{1A5276}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{1.02}

% Uniform list spacing (same gap above bullets everywhere)
\setlist[itemize]{leftmargin=1.4em, topsep=2pt, itemsep=2pt, parsep=0pt, partopsep=0pt}

% Uniform section heading style: UPPERCASE, accent, rule; equal spacing before/after
\titleformat{\section}{\large\bfseries\color{accent}}{}{0pt}{\MakeUppercase}[\vspace{-3pt}\titlerule]
\titlespacing*{\section}{0pt}{7pt}{3pt}

% Experience/Education entry: title (left) + date (right); role (left) + place (right)
\newcommand{\entry}[4]{%
  \vspace{3pt}%
  \textbf{#1}\hfill #2\par
  \vspace{1pt}%
  \textit{#3}\hfill \textit{#4}\par
  \vspace{2pt}%
}

\begin{document}

%================= HEADER =================
\begin{center}
  {\Huge \textbf{Shivam Gupta}}\\[4pt]
  {\color{accent}\textbf{Python Full Stack Developer}}\\[5pt]
  {\small
  \faMapMarker~Gwalior, M.P. \quad
  \faPhone~+91-8269699824 \quad
  \faEnvelope~\href{mailto:guptashivam93660@gmail.com}{guptashivam93660@gmail.com} \quad
  \faLinkedin~\href{https://www.linkedin.com/in/ur-990q}{LinkedIn} \quad
  \faGithub~\href{https://github.com/Shivam990q}{GitHub} \quad
  \faGlobe~\href{https://shivam-portfolio-a1s4.onrender.com}{Portfolio}}
\end{center}

%================= SUMMARY =================
\section{Summary}
Python full-stack developer skilled in \textbf{Python}, \textbf{Django/DRF}, \textbf{FastAPI},
and \textbf{React.js}/\textbf{Next.js}. Builds scalable REST APIs and responsive front-ends with
SQL database design, Docker, and CI/CD; multiple live products shipped.

%================= SKILLS =================
\section{Technical Skills}
\begin{itemize}[label={}, leftmargin=0pt, topsep=2pt, itemsep=2pt]
  \item \textbf{Languages:} Python, JavaScript (ES6+), TypeScript, SQL, Java, C, HTML5, CSS3
  \item \textbf{Backend \& Data:} Django, DRF, FastAPI, Node.js, REST APIs, Microservices, PostgreSQL, MongoDB
  \item \textbf{Frontend:} React.js, Next.js, Redux, React Query, Tailwind CSS, Responsive Design
  \item \textbf{Cloud, DevOps \& Tools:} AWS, Docker, CI/CD, Git \& GitHub, Postman, Agile/SDLC
  \item \textbf{AI (good to have):} LLMs, LangChain, CrewAI, MCP \& agents, Prompt Engineering
\end{itemize}

%================= EXPERIENCE =================
\section{Experience}
\entry{Full Stack Engineer (Intern)}{May 2025 -- Feb 2026}{ITM University, Gwalior}{On-site}
\begin{itemize}
  \item Redeveloping the university ERP with \textbf{React.js} and \textbf{Django REST APIs} ---
        building reusable, responsive front-end components for admin, examination, and quiz modules.
  \item Integrated REST endpoints for seamless front-end/back-end data flow; optimized FE
        performance for smooth, defect-free deployments.
\end{itemize}

\entry{WordPress Developer (Internship)}{Jul 2024 -- Aug 2024}{AdRyter Advertising}{On-site}
\begin{itemize}
  \item Built advanced, responsive websites and custom UI features using \textbf{React}, REST APIs,
        Gutenberg blocks, ACF, and headless WordPress.
\end{itemize}

\entry{Subject Matter Expert (Internship)}{Jan 2024 -- Aug 2024}{Solvitude Solutions (Brainly.com, US)}{Remote}
\begin{itemize}
  \item Delivered accurate, high-quality real-time technical solutions for the Brainly (US) platform.
\end{itemize}

%================= PROJECTS =================
\section{Projects}
\begin{itemize}
  \item \textbf{NETWORKED --- Live Web Platform} (\href{https://networkedconsultancy.com}{live})\\
        Full-stack platform: \textbf{Django REST} + PostgreSQL backend with a custom CMS and a \textbf{React + TypeScript} front-end; CI/CD to VPS.
  \item \textbf{ITMU Parakh Portal --- University MIS} (\href{https://parakh.itmuniversity.ac.in}{live})\\
        \textbf{Django REST} backend with a \textbf{React.js + Vite} front-end; admin, examination, and quiz modules.
  \item \textbf{Better Than Claude Skills} (\href{https://github.com/Shivam990q/better-than-claude-skills}{GitHub})\\
        \textbf{Python} toolkit of 16+ LLM agent skills with an MCP builder and a progressive-disclosure architecture.
  \item \textbf{CivicTrack --- Civic Issue Platform}\\
        Full-stack \textbf{React + Django} app for citizens to report and track local civic issues.
  \item \textbf{Open Figma MCP} (\href{https://github.com/Shivam990q/open-figma-mcp}{GitHub})\\
        MCP server that converts Figma designs into design tokens (8 formats) and generates UI code across 8 frameworks.
\end{itemize}

%================= ACHIEVEMENTS =================
\section{Achievements \& Leadership}
\begin{itemize}
  \item \textbf{President}, ITM Developers Club (IDC) --- led the team and organized tech events/talks.
  \item \textbf{Secured 3rd Position} --- Full Stack Development Bootcamp, ITM University (Dec 2025).
  \item \textbf{8th Rank (Solo)} --- Odoo Online Hackathon (qualified and competed solo).
  \item Certificate of Achievement, Google Developer Groups Solution Challenge 2025.
  \item \textbf{Top Performer --- Open Innovation}, Hacksagon 2025 (IEEE, ABV-IIITM Gwalior).
\end{itemize}

%================= EDUCATION =================
\section{Education}
\entry{B.Tech, Computer Science \& Engineering}{2023 -- 2027}{ITM University, Gwalior}{CGPA: 7.47}

%================= CERTIFICATIONS =================
\section{Certifications}
\begin{itemize}
  \item Full Stack Web Application Development with Django --- Udemy
  \item Postman API Fundamentals Student Expert --- Postman
  \item MongoDB Basics for Students --- MongoDB
  \item Career Essentials in Generative AI --- LinkedIn Learning
\end{itemize}

\end{document}
